---
title: "Section - Week 9"
author: "Juan Dodyk"
date: "11/9/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Miami-Dade voter file

We will use the `load()` function to load and `RData` file rather than a `csv`. This is useful for large data sets because `RData` files are able to compress the data to keep file sizes more manageable. When you use `load()`, you don't save it as anything using `<-`, but it will directly load an object into your R environment. In this case, it is a data frame called `dade`. 

```{r}
load("data/dade_vf_2020.RData")
```

| Variable   | Description                                           |
|:-----------|:------------------------------------------------------|
| `voter_id` | Voter ID number                                       |
| `city`     | City of residence                                     |
| `precinct` | Precinct of residence                                 |
| `race`     | Race of registered voter                              |
| `dem`      | 1=Democrat, 0=otherwise                               |
| `rep`      | 1=Republican, 0=otherwise                             |
| `female`   | 1=Female, 0=otherwise (Male/Unknown)                  |
| `age`      | Registrant age                                        |
| `PPP_2016` | 1 = Voted in 2016 presidential primary, 0=didn't vote |
| `PRI_2016` | 1 = Voted in 2016 state primary, 0=didn't vote        |
| `GEN_2016` | 1 = Voted in 2016 general election, 0=didn't vote     |


## Question 1

What proportion of Miami-Dade County registered voters are registered as Democrats? Take a sample of size 100 with replacement and calculate the sample mean. 

## Answer 1

```{r, q1}
mean(dade$dem)
```

```{r, q1_1}
sample_100 <- sample(dade$dem, size = 100, replace = TRUE)

mean(sample_100)
```


## Question 2

Take a sample of size 10, one of size 100, one of size 1,000, one of 5,000, one of 10,000, and one of 50,000 voters, and calculate the sample mean of `dem`.

What does the law of large numbers say about these sample means? Can you verify it in your experiment?

```{r, q2}
times <- c(10, 100, 1000, 5000, 10000, 50000)

results <- rep(NA, times = length(times))

for(i in 1:length(times)) {
  results[i] <- mean(sample(dade$dem, size = times[i], replace = TRUE))
}
results
```


## Question 3

If one considers the sum of `dem` in a random sample as a random variable, how is its probability distribution called? Calculate its mean, its variance and its standard deviation using a formula that depends only on the number of voters that are sampled, $n$.

## Answer 3

The sample mean is distrusted as a binomial variable with size 10 and success probability 0.41. 

mean: n * p

Variance: n * p * (1-p)

Standard deviation: sqrt(n * p * (1-p))

## Question 4

Calculate the mean, the variance and the standard deviation of the mean of `dem` in a random sample of $n$ voters. You may need to review the lecture http://gov51.mattblackwell.org/slides/videos/24-mean-var.pdf

```{r}
E(X/n) = E(X) / n = p * n / n = p

V(X/n) = V(1/n * X) = (1/n)^2 * V(X) = 1/n^2 * p * (1-p) * n = p * (1-p) / n

Therefore variance becomes smaller once sample gets larger -> quantitative version of the law of large numbers

SD = sqrt(0.24 / n)
```


## Question 5

Knowing the probability distribution of the sample mean, we want to take 2,000 samples from that distribution, assuming that we sampled 10 voters from the voter file. Create a histogram showing the distribution of these sample means.

Distribution of the sample mean = Binomial(size = n, prob = 0.41) / n

```{r, q5}
hist(rbinom(2000, size = 10, prob = 0.41) / 10)
```


## Question 6

Repeat the above exercise for 100 voters, 1,000 voters, and 10,000 voters.

What does the central limit theorem say about these distributions? Does it hold in your experiment?

```{r, q6}
hist(rbinom(2000, size = 100, prob = 0.41) / 100)
hist(rbinom(2000, size = 1000, prob = 0.41) / 1000)
hist(rbinom(2000, size = 10000, prob = 0.41) / 10000)
```

Central Limit Theorem: The distribution of the sample mean will be closer and closer to a normal distribution with mean 0.41 and standard deviation 0.49/sqrt(n) as n increases.
